\documentclass[10pt]{article}
\usepackage[margin=0.42in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage{needspace}

% Fonts: Times New Roman for body, Young Serif for name
\defaultfontfeatures{Ligatures=TeX}
\IfFontExistsTF{Times New Roman}
  {\setmainfont{Times New Roman}[Scale=0.98]}
  {\setmainfont{TeX Gyre Termes}[Scale=1.0]}
\newfontfamily\youngserif{YoungSerif-Regular.ttf}[
  Path=./fonts/,
  BoldFont=YoungSerif-Bold.ttf,
  ItalicFont=YoungSerif-RegularItalic.ttf,
  BoldItalicFont=YoungSerif-BoldItalic.ttf
]
\newfontfamily\youngseriflight{YoungSerif-Light.ttf}[
  Path=./fonts/,
  BoldFont=YoungSerif-Regular.ttf,
  ItalicFont=YoungSerif-LightItalic.ttf,
  BoldItalicFont=YoungSerif-RegularItalic.ttf
]

% Color palettes
\definecolor{Accent}{HTML}{4A7C3F}
\definecolor{Slate}{HTML}{4A5568}
\definecolor{Body}{HTML}{111827}

\hypersetup{
  colorlinks=true,
  urlcolor=Accent,
  linkcolor=Accent,
  pageanchor=false
}

% Global spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\raggedbottom
\widowpenalty=10000
\clubpenalty=10000
\displaywidowpenalty=10000
\color{Body}

% Section formatting — Young Serif
\titleformat{\section}
  {\youngserif\bfseries\large\color{Accent}}
  {}{0em}{}
  [{\color{Accent}\titlerule}]
\titlespacing{\section}{0pt}{4pt}{3pt}

% Item spacing
\setlist[itemize]{
  leftmargin=*,
  label=-,
  itemsep=0pt,
  topsep=1pt,
  parsep=0pt,
  partopsep=0pt
}

% No page numbers
\pagenumbering{gobble}

% Role headings: Young Serif bold
\newcommand{\Role}[1]{{\youngserif\bfseries #1}}
\newcommand{\EntryGap}{\vspace{0pt}}
\newcommand{\ResumeSection}[1]{\Needspace{6\baselineskip}\section*{#1}}

% Pipe + italic meta addendum: Young Serif italic
\newcommand{\Meta}[1]{{\youngserif\textbar{}\ \itshape\color{Slate}#1}}
\newcommand{\Date}[1]{{\youngserif\bfseries #1}}
\newcommand{\Tech}[1]{{\itshape Technologies:} #1}
\newcommand{\Action}[1]{{\color{Accent}#1}}
\newcommand{\Narrative}[1]{{\color{Body}#1}}

\begin{document}
\fontsize{9.4}{10.9}\selectfont

\begin{minipage}[b]{0.40\linewidth}
{\youngserif\fontsize{38}{40}\selectfont\bfseries\color{Accent} Jakob Langtry}
\end{minipage}%
\hfill
\begin{minipage}[b]{0.57\linewidth}
\raggedleft
{\youngseriflight\small\color{Body}
{\color{Accent}\faEnvelope}\ \href{mailto:jjalangtry@gmail.com}{ jjalangtry@gmail.com} \,|\,
{\color{Accent}\faPhone\ (607) 731-5440} \\
{\color{Accent}\faGithub}\ \href{https://github.com/jjalangtry}{github.com/jjalangtry} \,|\,
{\color{Accent}\faLinkedinIn}\ \href{https://linkedin.com/in/jjalangtry}{linkedin/jjalangtry} \,|\,
{\color{Accent}\faGlobe}\ \href{https://jjalangtry.com}{jjalangtry.com}}
\end{minipage}
{\color{Accent}\rule{\linewidth}{0.8pt}}

\vspace{2pt}
{\youngseriflight\small\color{Slate} Full-stack software engineer building web and embedded systems, from shipping product features to debugging networked devices, with leadership experience as President of the RIT Society of Software Engineers.}
\vspace{-1pt}

\ResumeSection{Education}
{\youngserif\bfseries Rochester Institute of Technology} \Meta{B.S. Software Engineering} \hfill \Date{May 2026} \\
{\youngserif\bfseries Corning Community College} \Meta{A.S. Computer Science} \hfill \Date{Dec 2021}

\ResumeSection{Experience}
{\Role{WeTheHobby \Meta{Software Engineering Co-op}}} \hfill \Date{Jun 2025 -- Present} \\
\Tech{React, TypeScript, C\#, .NET, ASP.NET Core, MUI, AWS, SQL, Streaming Infrastructure, Cursor}
\begin{itemize}
  \item \Action{Architected an admin user-management UI and CQRS refactor;} \Narrative{eliminated manual database user creation from internal operations.}
  \item \Action{Deployed I/O virtualization across the streaming stack;} \Narrative{cut stream recovery from 5 minutes of dead air to \textasciitilde{}30 seconds and removed single points of failure.}
  \item \Action{Implemented Markdown description editing across the product;} \Narrative{added editable and bulk-editable flows via a custom \texttt{IDescribable} interface.}
  \item \Action{Shipped across frontend, backend, and streaming systems;} \Narrative{worked end-to-end in a fast-moving startup environment.}
\end{itemize}
\EntryGap

{\Role{Precision Optical Technologies (Purchased by Belden) \Meta{Software Engineering Co-op}}} \hfill \Date{Aug 2024 -- May 2025} \\
\Tech{C, C++, Make, Unix, Netconf, RPC, SNMP, Optical Networking, YANG}
\begin{itemize}
  \item \Action{Enabled breakout mode for QSFP NNI ports;} \Narrative{migrated SNMP tables to 2.0 OID range.}
  \item \Action{Created polling worker monitoring admin state/transceiver presence;} \Narrative{triggered alarms and LED state updates.}
  \item \Action{Replaced fan control code with synchronized bank selects;} \Narrative{reduced fan noise and improved reliability.}
\end{itemize}
\EntryGap

{\Role{Apple, Inc. \Meta{Product Specialist}}} \hfill \Date{Oct 2023 -- Feb 2024}
\begin{itemize}
  \item \Action{Learned critical time management;} \Narrative{handled dense part-time work while attending school full-time.}
  \item \Action{Assisted customers daily with device setup and tailored solutions;} \Narrative{consistently hitting sales targets.}
\end{itemize}
\EntryGap

{\Role{Hardinge, Inc. \Meta{IT/Computer Science Intern}}} \hfill \Date{Jun 2021 -- Aug 2021}
\begin{itemize}
  \item \Action{Built software-vendor metrics tooling on legacy systems as the sole programmer on the initiative.}
  \item \Action{Deployed an automated PowerPoint rotation system to dozens of factory TVs;} \Narrative{improved consistency for plant-wide communication.}
  \item \Action{Provided IT helpdesk support to hundreds of employees each month.}
\end{itemize}

\ResumeSection{Leadership}
{\Role{President \Meta{RIT Society of Software Engineers}}} \hfill \Date{Aug 2024 -- May 2025}
\begin{itemize}
  \item \Action{Finished the rework of sse.rit.edu;} \Narrative{replacing CampusGroups and Google Drive for club management.}
  \item \Action{Bolstered alumni relations;} \Narrative{got hundreds of alumni from 2005-2025 to put their contact information on the website.}
  \item \Action{Secured lab renovation;} \Narrative{won approvals despite red tape for a \$40,000, five-year project modernizing the member space.}
\end{itemize}

\ResumeSection{Projects}
{\Role{BeyondRGB \Meta{RIT Senior Project (Open Source)}}} \hfill \Date{Oct 2025 -- May 2026} \\
\Tech{C++, Electron, React, TypeScript, CMake, vcpkg}
\begin{itemize}
  \item \Action{Debugged blob memory leaks and backend error propagation in a spectral imaging desktop app for museum art archiving (43 stars);} \Narrative{also shipped drag-and-drop import, OS-synced theming, and a settings UI refactor.}
\end{itemize}
\EntryGap

{\Role{TheSSEquel \Meta{sse.rit.edu}}} \hfill \Date{Jan 2026 -- Present} \\
\Tech{Next.js, TypeScript, Prisma, NextAuth, Tailwind CSS, PostgreSQL}
\begin{itemize}
  \item \Action{Shipped production features for the RIT SSE website;} \Narrative{built role-based OAuth scopes, invite flow, event and attendance tooling, mentoring fixes, mobile fixes, and mass-email improvements.}
\end{itemize}
\EntryGap

{\Role{ReadFaster \Meta{Personal Project}}} \hfill \Date{Jan 2026 -- Feb 2026} \\
\Tech{Swift, SwiftUI, SwiftData, PDFKit, SwiftSoup}
\begin{itemize}
  \item \Action{Built RSVP speed-reading app for iOS/macOS;} \Narrative{TXT/EPUB/PDF support, adaptive pacing, chapter navigation, and comprehension-focused controls.}
\end{itemize}

{\Role{Delegative Strategy Game \Meta{Personal Project}}} \hfill \Date{Dec 2025 -- Jan 2026} \\
\Tech{Python, Textual, Rich, Pydantic, HTTPX, Agentic Tool Calling, OpenRouter API}
\begin{itemize}
  \item \Action{Built an agentic strategy game framework;} \Narrative{the model creates and updates world state from natural-language player interactions through tool calling.}
\end{itemize}
\EntryGap

{\Role{Playlist Converter \Meta{Personal Project}}} \hfill \Date{Nov 2025 -- Dec 2025} \\
\Tech{Next.js, React, TypeScript, Tailwind CSS, PostgreSQL, Drizzle ORM, Spotify OAuth, Apple MusicKit}
\begin{itemize}
  \item \Action{Built Spotify/Apple Music playlist conversion;} \Narrative{ISRC matching, fuzzy fallback, manual matching, and shareable expiring links.}
\end{itemize}

\ResumeSection{Skills}
{\youngserif\bfseries Languages:} TypeScript, C++, C, C\#, Swift, Python, SQL, JavaScript, Java, Lua, Assembly \\
{\youngserif\bfseries Frameworks \& Libraries:} React, Next.js, .NET, ASP.NET Core, Prisma, Drizzle ORM, Electron, SwiftUI, Tailwind CSS, MUI, ShadCN UI, Angular, Vue \\
{\youngserif\bfseries Data \& Backend:} PostgreSQL, MySQL, REST APIs \\
{\youngserif\bfseries Systems \& Networking:} Netconf/YANG, SNMP, RPC, Optical Networking, Streaming Infrastructure \\
{\youngserif\bfseries Cloud \& Tooling:} AWS, Terraform, CI/CD, Unix/Linux, Git, Make, Maven, Cursor

\end{document}
